---
title: "Project Proposal"
author: "Bea De Oliveira, Jess Chen, Brendan Kelleher, Etan MacLean"
date: "3-22-2021"
output: pdf_document
---

```{r load}
library(tidyverse)
```

```{r fight-data, warning = FALSE, message = FALSE}
fight_songs <- read.csv("fight-songs.csv")
glimpse(fight_songs)
```

make sure the printing of code chunks is turned off with the option echo = FALSE.
Your final written report should not exceed five pages inclusive of all tables and figures
overwrite notre dame data to be in ACC

data descriptors: https://github.com/fivethirtyeight/data/tree/master/fight-songs/

**Dataset on Fight Songs**

Random observations:

- Some fight songs are just named "___ fight song"
- boxplots of eras fight songs were written in (faceted by decade)
- does vocab change w student writer? does it correlate with if the song is official?
- BPM and duration as continuous variables
- measures of aggressiveness of time (rah, BPM, number_fights)

Overall question: intensity over time
Look at BPM, trope_count (investigate distributions of constituent variables such as rah),
Substudy: are intense songs longer in duration?
Graphs could look at individual distributions of response variables

boxplots
histograms
scatterplots by color
pie charts
linear models
facet grids
bar charts / filled bar charts by color

1. ETAN: Boxplot with trope_count as one color and its sub-variables (rah, men, spelling, nonsense) as adjacent boxplots


2. Something w BPM

```{r}
bpm_songs <- fight_songs %>%
  group_by(year) %>%
  summarize(avg_bpm = mean(bpm))
bpm_songs %>% 
  ggplot() +
  scale_x_discrete(guide = guide_axis(n.dodge=4)) +
  geom_col(mapping = aes(x = year, y = avg_bpm)) +
  labs(title = "Relationship Between Year and Average Song BPM", 
       x = "Year", y = "Average BPM") +
  theme_bw()
```


3. LM of time vs. BPM and LM of time vs. trope_count - which predicts better? (use adj.r.squared)

4. Make LM of time vs. intensity (mutate new variable)

Look at how the LM works in different areas (does time predict trope_count or BPM better)

Mutate new variable, intensity, which combines BPM and trope_count
- Use boxplots to find factor to adjust trope_count to match BPM range; then combine
Final model: linear regression w time as explanatory and intensity as response

## Introduction

The introduction provides motivation and context for your research. Describe your topic (citing sources) and provide a concise, clear statement of your research question and hypotheses.

Then identify the source of the data, when and how it was collected, the cases, a general description of relevant variables.

## Methodology

The methodology section should include visualizations and summary statistics relevant to your research question. You should also justify the choice of statistical method(s) used to answer your research question.

## Results

Showcase how you arrived at answers to your research question using the techniques we have learned in class (and beyond, if you’re feeling adventurous).

Provide only the main results from your analysis. The goal is not to do an exhaustive data analysis (calculate every possible statistic and perform every possible procedure for all variables). Rather, you should demonstrate that you are proficient at asking meaningful questions and answering them using data, that you are skilled in interpreting and presenting results, and that you can accomplish these tasks using R. More is not better.

## Discussion

This section is a conclusion and discussion. This will require a summary of what you have learned about your research question along with statistical arguments supporting your conclusions. You should critique your own methods and provide suggestions for improving your analysis and future work. Issues pertaining to the reliability and validity of your data and the appropriateness of the statistical analyses should also be discussed. Also include a brief paragraph on what you would do differently if you were able to start over with the project.






Research Topic: The data set works to analyze Collegiate fight songs over time and the elements contained in each song (distance, violence, words, etc).

Research Question: How does the intensity (tropes, BPM) of fight songs change over time? How does this change based on geography?

Hypothesis: Fight songs have gotten shorter and more aggressive over time.

